%%
%% Author: Tim
%% 2018-06-05
%%

\section{Glossary}
\textbf{Maramafication (M):} plural Ms;
\vspace{2mm}\\ %2mm vertical space
\textbf{M-constructor block (M-block):}
\vspace{2mm}\\
\textbf{Maramafication-designer (MD):} a person who designs new maramafications of a given set of programming constructs of a given programming language.
\vspace{2mm}\\
\textbf{Maramafication-gamer (MG):} is a maramafication-designer who lets his or her maramafications compete with other maramafications via a serious marama game. The maramafication-gamer is not the person designing the puzzles (i.e. the Maramafication-game-designer). An analogy is a designer of a solar car. He or she may choose to let his car (maramafication) compete at the World Solar Challenge (marama game), however, he is not the designer/organiser of the competition (the puzzles).
\vspace{2mm}\\
\textbf{Marama-gamer:}
\vspace{2mm}\\
\textbf{Maramafication-game-designer (MGD):} a person who designs aspects of the serious game around Maramafications. The relation between a Maramafication-gamer and a Maramafication-game-designer is clarified in the glossary-item about Maramafication-gamer. There are a few sub-categories of such designers, amongst which the Maramafication-puzzle-designer.
\vspace{2mm}\\
\textbf{Maramafication-puzzle-designer (MPD):} a maramafication-game-designer who designs puzzles for the serious marama game.
\vspace{2mm}\\
\textbf{Marama-transpiler:} An application that transpiles the textual source language together with a configuration file (for example in JSON or XML) to a maramfication.
\vspace{2mm}\\
\textbf{Marama-transpiler:} this is the transpiler that is currently being developed for a specific maramification, written in Haskell etc.
\vspace{2mm}\\
\textbf{Programming construct:} a part of the syntax of a programming language that can be considered as a building block to write programs in that language. Examples of language constructs are type definitions, function definitions, type declarations, function applications, switch-case statements, class-definitions and if-statements.
\vspace{2mm}\\
\textbf{Maramification-behaviour (MB):} a configuration that determines the way the Ms will react to each other
\vspace{2mm}\\
\textbf{Marama-view application (MVA):} the 3D graphical scene and interface of the MEA.
\vspace{2mm}\\
\textbf{Marama-editor application (MEA):} the application in which the puzzles for the marama game can be created and changed.
\vspace{2mm}\\
\textbf{Marama-game application (MGA):} the application used to solve marama puzzles.

\newpage